Stochastic Wind Power Forecasting

### 2020-04-14 LaTeX_Code/Paper/paper_1line.tex
approximate likelihoods

Remark: {\color{red} Observe that a mean-reverting model without derivative tracking shows a delayed path behavior. For instance, consider the diffusion model (\ref{eq:main}) with $a(X_t; p_t, \bm{\theta}) = - \theta_0 (X_t - p_t)\,, \theta_0 > 0$. In this case, given  $ \mathbb{E} X_0 = p_0$, the diffusion has mean $\mathbb{E} X_t = p_t - e^{- \theta_0 t } \int_0^t \dot{p}_s  e^{\theta_0 s} ds$. The next Figure (\ref{fig:derivative_tracking}) illustrates paths of two diffusions with and without derivative tracking. }

\begin{figure}[h]
  %\includegraphics[width=26mm,scale=1]{}
  \caption{Add Figure showing the difference with and without derivative tracking}
  \label{fig:derivative_tracking}
\end{figure}

@@

{\color{red}We can see in Figure (\ref{fig:LP_transitions}) the effect of the Lamperti transformation upon the forecast error data.

@@

@@

>>>>

Remark: Observe that a mean-reverting model without derivative tracking shows a delayed path behavior. For instance, consider the diffusion model (\ref{eq:main}) with $a(X_t; p_t, \bm{\theta}) = - \theta_0 (X_t - p_t)\,, \theta_0 > 0$. In this case, given  $ \mathbb{E} X_0 = p_0$, the diffusion has mean $\mathbb{E} X_t = p_t - e^{- \theta_0 t } \int_0^t \dot{p}_s  e^{\theta_0 s} ds$. The next Figure (\ref{fig:derivative_tracking}) illustrates paths of two diffusions with and without derivative tracking.

\begin{figure}[h]
  %\includegraphics[width=26mm,scale=1]{}
  \caption{{\color{red} Add Figure showing the difference with and without derivative tracking}}
  \label{fig:derivative_tracking}
\end{figure}

@@

{\color{red} We can see in Figure (\ref{fig:LP_transitions}) the effect of the Lamperti transformation upon the forecast error data.

@@

The approximate log-likelihood $\tilde{\ell}(\cdot ; v^{V, N+1})$ of the observed sample $v^{V, N+1}$ can be expressed as 
\begin{equation}
 \tilde{\ell} (\bm{\theta}; v^{M,N +1}) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1, \xi_2)} \Big( \frac{z_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \Big)^{\xi_1 -1}  \Big( \frac{1 - \epsilon - z_{j,i}}{2(1 - \epsilon)} \Big)^{\xi_2 -1} \right\} \,,
\label{loglikelihoodV}
\end{equation}
where the shape parameters $\xi_1$ and $\xi_2$, according to (\ref{param_transformed_beta}), depend on the quantities $\mu(t_{j,i};\bm{\theta} )$ and $\sigma^2(t_{j,i};\bm{\theta} )$ that are computed solving numerically the initial-value problem (\ref{Vtmom}). \\

@@

The approximate log-likelihood $\tilde{\ell}(\cdot ; z^{V, N+1})$ of the observed sample $z^{V, N+1}$ is given by
\begin{equation}
\tilde{\ell} (\bm{\theta}; z^{M,N +1}) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i};\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}; \bm{\theta})} \Bigg) \right\}   \,,   \label{loglikelihoodZ}
\end{equation}
where $\tilde{\mu}_Z(t_{j,i};\bm{\theta} )$ and $\tilde{v}_Z(t_{j,i};\bm{\theta} )$ are computed solving numerically the initial-value problem (\ref{Ztmom}).
